Lossy compression of DNA sequencing quality data

### 2016-04-18 bmc_manuscript/manuscript.tex
Fixed a reference, revised some text, and added a note (in red) where more text is needed.

\cite{Wan:2012kq} provide three similar lossy compression strategies
based on binning the base error probability distribution: UniBinning,
Truncating, and LogBinning. UniBinning evenly splits the error
probability distribution into a user-defined number of partitions.
Truncating treats a user-defined number of highest quality values as a
single bin. LogBinning works similarly to UniBinning, except it uses
the \emph{log} of the error probability distribution, which
effectively bins the \textsc{ascii} quality values evenly. The 2-bin
encoding examined here can be viewed as something like a combination
of LogBinning and Truncating in that we place the highest quality
values (as defined above) from the distribution of log error
probability values into a single bin.

@@

For comparison to other developed methods we use \textsc{QualComp}, a
lossy compression tool~\cite{Ochoa:2013rt}. The program models quality
values as a multivariate Gaussian distribution, computing the mean and
covariance for each position in the read, and these values are stored
by the decoder to later reconstruct a \emph{representative} quality
value. \textsc{QualComp} takes as input a user-specified rate
(bits/read), and these bits are apportioned among positions within the
read to minimize the average error. The quality values can be
clustered beforehand to produce more accurate models.

@@

>>>>

Previous work by others \cite{Wan:2012kq} describe three similar lossy
compression strategies based on binning the base error probability
distribution: UniBinning, Truncating, and LogBinning. UniBinning
evenly splits the error probability distribution into a user-defined
number of partitions.  Truncating treats a user-defined number of
highest quality values as a single bin. LogBinning works similarly to
UniBinning, except it uses the \emph{log} of the error probability
distribution, which effectively bins the \textsc{ascii} quality values
evenly. The 2-bin encoding examined here can be viewed as something
like a combination of LogBinning and Truncating in that we place the
highest quality values (as defined above) from the distribution of log
error probability values into a single bin.

@@

For comparison to other developed methods for lossy compression of
quality values we analyzed the reference data with
\textsc{QualComp}~\cite{Ochoa:2013rt},
\textsc{rsa}~\cite{DBLP:conf/recomb/YuYB14}, and
\textsc{qvz}~\cite{Malysa01102015}.

\textsc{QualComp} models quality values as a multivariate Gaussian
distribution, computing the mean and covariance for each position in
the read, and these values are stored by the decoder to later
reconstruct a \emph{representative} quality value. \textsc{QualComp}
takes as input a user-specified rate (bits/read), and these bits are
apportioned among positions within the read to minimize the average
error. The quality values can be clustered beforehand to produce more
accurate models.

@@

\textcolor{red}{Add brief description of \textsc{rsa} and
  \textsc{qvz}, including economic costs.}
